$\pi$SOD-M: A Methodology for Building Service-Oriented Applications in the Presence of Non-Functional Properties

### 2013-10-30 JournalToSubmit2013/modelingFlyingPig.tex
no message

Figure \ref{fig:E3valuemodel} shows the BPMN model  \footnote{Details on BPMN (Business Process Management Notation) can be found in http://www.bpmn.org/} of the scenario.

@@

\begin{figure}
\centering
\includegraphics[width=0.55\textwidth]{figs/SC}
\caption{BPMN model of the "To Publish Music" scenario}
\label{fig:E3valuemodel}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=1\textwidth]{figs/ValueModel_GCP}
\caption{E3value model of the FlyingPig scenario}
\label{fig:E3valuemodel}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=1\textwidth]{figs/BPMN_GCP.png}
\caption{BPMN model of the FlyingPig scenario}
\label{fig:bpmn}
\end{figure}

Figure \ref{fig:bpmn} shows the BPMN model  \footnote{Details on BPMN (Business Process Management Notation) can be found in http://www.bpmn.org/} of the scenario.

@@
